Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Latest

\begin{quote}
\begin{itemize}
\item Can you think of a fix to the program?  You can try it out and see
if it works or not.
\end{itemize}
\end{quote}

@@

@@

\begin{enumerate}
\item CXL programs can usually be easily translated into Python.  For example,
Figure~\ref{fig:incpy} is a Python version of Figure~\ref{fig:inc}.
\begin{enumerate}
\item Run Figure~\ref{fig:incpy} using Python.  Does the assertion fail?
\item Using a script, run Figure~\ref{fig:inc} 1000 times.  How many times does the assertion
fail (if any).
\end{enumerate}
\item Figure~\ref{fig:incmany} is a version of Figure~\ref{fig:incpy} that has each
incrementer thread increment \texttt{count} \texttt{N} times.  Run Figure~\ref{fig:incpy}
10 times (using Python).
Report how many times the assertion fails and what the value of \texttt{count}
was for each of the failed runs.
\end{enumerate}

@@

\chapter{Reader/Writer Locks, Part 2}
\label{ch:rdwr2}

>>>>

@@

The following exercises are intended to show you that on the one hand it
is easy to translate CXL programs into Python, but on the other hand,
it is easier to find concurrency bugs using CXL.

@@

\begin{enumerate}
\item CXL programs can usually be easily translated into Python.  For example,
Figure~\ref{fig:incpy} is a Python version of Figure~\ref{fig:inc}.
\begin{enumerate}
\item Run Figure~\ref{fig:incpy} using Python.  Does the assertion fail?
\item Using a script, run Figure~\ref{fig:incpy} 1000 times.  How many times does the assertion
fail (if any).
\end{enumerate}
\item Figure~\ref{fig:incmany} is a version of Figure~\ref{fig:incpy} that has each
incrementer thread increment \texttt{count} \texttt{N} times.  Run Figure~\ref{fig:incpy}
10 times (using Python).
Report how many times the assertion fails and what the value of \texttt{count}
was for each of the failed runs.
\item Can you think of a fix to Figure~\ref{fig:inc}?  Try one or two different fixes
and run them through CXL.  Do not worry about having to come up with a correct fix at this
time---the important thing is to develop an understanding of concurrency.
\end{enumerate}

@@

\chapter{Reader/Writer Locks with Blocking}
\label{ch:rdwr2}
